---
title: "CECL"
file:	vecm.rmd
author: Yusuf Saib
date: "08/20/2017"
output: html_document
---

<a href="javascript:history.back()">Go Back</a>

##################################################### 
# The optimal lag structure # 
##################################################### 

#### VarSelect result
```{r, echo = FALSE}
print(varModel)
```

##################################################### 
# RESULT OF VECM MODEL # 
##################################################### 

#### 1. Conduct EIGEN test: ecdet=NONE -------- spec=TRANSITORY
```{r, echo = FALSE}
print(summary(vecm_ct_eigen_trans_none))
```
#### 2. Conduct EIGEN test: ecdet=CONST -------- spec=TRANSITORY
```{r, echo = FALSE}
print(summary(vecm_ct_eigen_trans_const))
```

#### 3. Conduct EIGEN test: ecdet=TREND -------- spec=TRANSITORY
```{r, echo = FALSE}
print(summary(vecm_ct_eigen_trans_trend))
```

#### 4. Conduct EIGEN test: ecdet=NONE -------- spec=LONGRUN
```{r, echo = FALSE}
print(summary(vecm_ct_eigen_lr_none))
```
#### 5. Conduct EIGEN test: ecdet=CONST -------- spec=LONGRUN
```{r, echo = FALSE}
print(summary(vecm_ct_eigen_lr_const))
```

#### 6. Conduct EIGEN test: ecdet=TREND -------- spec=LONGRUN
```{r, echo = FALSE}
print(summary(vecm_ct_eigen_lr_trend))
```



#### 7. Conduct Trace test: ecdet=NONE -------- spec=TRANSITORY
```{r, echo = FALSE}
print(summary(vecm_ct_trace_trans_none))
```
#### 8. Conduct Trace test: ecdet=CONST -------- spec=TRANSITORY
```{r, echo = FALSE}
print(summary(vecm_ct_trace_trans_const))
```

#### 9. Conduct Trace test: ecdet=TREND -------- spec=TRANSITORY
```{r, echo = FALSE}
print(summary(vecm_ct_trace_trans_trend))
```

#### 10. Conduct Trace test: ecdet=NONE -------- spec=LONGRUN
```{r, echo = FALSE}
print(summary(vecm_ct_trace_lr_none))
```
#### 11. Conduct Trace test: ecdet=CONST -------- spec=LONGRUN
```{r, echo = FALSE}
print(summary(vecm_ct_trace_lr_const))
```

#### 12. Conduct Trace test: ecdet=TREND -------- spec=LONGRUN
```{r, echo = FALSE}
print(summary(vecm_ct_trace_lr_trend))
```
